The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-04-03 exp-resurgence.tex
Commit detailed version of third-order thimble integrals

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
\end{enumerate}
\begin{center}
\basicLaplace
\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
\end{center}

@@

The Borel summation process is summarized in the following diagram:
\begin{center}
\begin{tikzcd}
& \text{problem} & \\
\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
& & \\
\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
\end{tikzcd}
\end{center}

@@

%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray. We will call it {\em Borel regularization}.
%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information. We will call this process {\em Borel regularization}.
%\begin{itemize}
%\item We will say $\Phi$ is {\em Borel-regularizable} if it is asymptotic to a Borel-summable power series.
%\item We will say $\Phi$ is {\em Borel regular} if it is Borel-regularizable and Borel regularization leaves it unchanged.
%\item We have the following vector space inclusions:
%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there is a constant $c \in (0, \infty)$ with
%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
%
%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
%\begin{itemize}
%\item $\Phi$ is Borel regular.
%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
%\item $\phi$ grows at most exponentially along the Laplace transform ray.
%\end{itemize}
%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible. \textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion. Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e. it is Borel regular)? P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type. In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function. When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
%\item \ldots
%\end{itemize}

@@

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
\begin{theorem}\label{thm:exist_uniq_ODE}
Let $-\alpha$ be a root of $P$. Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \right] \]
of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}\label{thm:soln_is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of the suitable normalizad formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
\end{theorem}
We can use this result to show that $\Psi_\alpha$ is Borel regular. Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:shifted_holo_closed} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
\color{RoyalBlue}
\begin{theorem}\label{thm:soln_is_asymptotic}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{theorem}
\color{black}
\begin{corollary}\label{cor:soln_borel-reg}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular. This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{corollary}
In many cases, by choosing from among the solutions $\Psi_\alpha$, we can build a frame of Borel-regular solutions of the equation $\mathcal{P}\Phi = 0$.

@@

\item\label{part-2} The Borel transform $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
\item\label{part-3} The sum of $\tilde{\iota}_\alpha$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$. Its Laplace transform along that ray is well-defined, and equal to $I_\alpha$.

@@

 %   Let $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:

@@

%\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
%\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.

@@

%{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}\arrow[dd,"\borel"]\\

@@

%\iota \arrow[r,equal] & \hat{\iota} & &\tilde{\iota} \arrow[ll, "\text{sum}"]

@@

On the other hand, we compute the asymptotic expansion of $I$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain. Consequently, its Borel transform $\series{\iota}$ is a germ of holomorphic functions at $\zeta=\alpha$ in the position domain. Finally, we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\tilde{\iota}$.

@@

%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}

@@

%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket

@@

%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 

@@

%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\

@@

%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]

@@

%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\

@@

%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]

@@

%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular. Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity. Hence $\Phi$ is Borel-regularizable. In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$. In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity. 
\subsection{Borel regularity for level~$1$ ODEs}
%
The study of irregular singular differential equations in the complex domain has a long history, and interesting phenoma distinguish irregular singular equations to regular singular ones. Already at the formal level, irregular singular ODEs have a distinguished behaviour, namely they admit divergent formal series solutions in the form of trans-monomials. In particular, for level $1$ ODEs of the kind we study in this paper, the Poincar\'e method gives an algorithm to compute formal solutions of $\mathcal{P}\Phi=0$, see~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Then, the main question is how to ``promote'' a formal solution to an analytic one, and here is where summability methods will play a r\^ole~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}. In fact, even if it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one (see~\cite[Chapter 14]{balser}). Then, the Ramis Index Theorem shows that the formal solutions $\tilde{\Phi}$ of $\mathcal{P}\Phi=0$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.  \textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]} Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.

@@

\color{RoyalBlue}
From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Since the cirtical values are distinct, the transmonomials $\tilde{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame. Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}). To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}. For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}. \textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]}

At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame. This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\tilde{\Psi}_\alpha$ (see Theorem~\ref{thm:soln_is_asymptotic}). Recall that the key aspect in the proof of our result~\cite[Theorem~4]{reg-sing-volterra} is going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$. Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange solves differential equations analytically in the position domain~\cite{malgrange--fourier}, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).

@@

When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound

@@

    \[\borel_\zeta(\tilde{\Phi}\tilde{\Psi})=\borel_\zeta\tilde{\Phi}\ast\borel_\zeta\tilde{\Psi}.\]

@@

&=\borel_\zeta\tilde{\Phi}\ast \borel_\zeta\tilde{\Psi}\,.

@@

\begin{theorem}\label{thm:maxim-proof}

@@

\textcolor{orange}{[Change statement as in Intoduction]}

@@

\begin{figure}
\center

>>>>

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\series{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
\end{enumerate}
\begin{center}
\basicLaplace
\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
\end{center}

@@

The Borel summation process is summarized in the following diagram:
\begin{center}
\begin{tikzcd}
& \text{problem} & \\
\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
& & \\
\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
\end{tikzcd}
\end{center}

@@

%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray. We will call it {\em Borel regularization}.
%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information. We will call this process {\em Borel regularization}.
%\begin{itemize}
%\item We will say $\Phi$ is {\em Borel-regularizable} if it is asymptotic to a Borel-summable power series.
%\item We will say $\Phi$ is {\em Borel regular} if it is Borel-regularizable and Borel regularization leaves it unchanged.
%\item We have the following vector space inclusions:
%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there is a constant $c \in (0, \infty)$ with
%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
%
%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
%\begin{itemize}
%\item $\Phi$ is Borel regular.
%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
%\item $\phi$ grows at most exponentially along the Laplace transform ray.
%\end{itemize}
%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible. \textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion. Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\series{\Phi}$ and $\series{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\series{\Phi}$ (i.e. it is Borel regular)? P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\series{\Phi}$, then $\series{\Phi}$ is of Gevrey type. In addition, every Gevrey type series $\series{\Phi}$ is the Gevrey asymptotics of a holomorphic function. When it is defined, the Borel sum of $\series{\Phi}$ is the natural holomorphic function asymptotic to $\series{\Phi}$.]}
%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
%\item \ldots
%\end{itemize}

@@

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
\begin{theorem}\label{thm:exist_uniq_ODE}
Let $-\alpha$ be a root of $P$. Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha) \right] \]
of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\widehat{\Omega}_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}\label{thm:soln_is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of the suitable normalizad formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
\end{theorem}
We can use this result to show that $\Psi_\alpha$ is Borel regular. Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:shifted_holo_closed} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
\color{RoyalBlue}
\begin{theorem}\label{thm:soln_is_asymptotic}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{theorem}
\color{black}
\begin{corollary}\label{cor:soln_borel-reg}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular. This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{corollary}
In many cases, by choosing from among the solutions $\Psi_\alpha$, we can build a frame of Borel-regular solutions of the equation $\mathcal{P}\Phi = 0$.

@@

\item\label{part-2} The Borel transform $\series{\iota}_\alpha \defeq \borel_\zeta \series{I}_\alpha$ converges near $\zeta=\alpha$.
\item\label{part-3} The sum of $\series{\iota}_\alpha$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$. Its Laplace transform along that ray is well-defined, and equal to $I_\alpha$.

@@

 %   Let $\series{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:

@@

%\item The series $\series{\Phi}_j:=z^{1/2} \series{I}_j$ is $1$-Gevrey, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\series{\Phi}_j)$ converges near $\zeta=\alpha_j$
%\item If you continue the sum of $\series{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.

@@

%{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \series{I}\arrow[dd,"\borel"]\\

@@

%\iota \arrow[r,equal] & \hat{\iota} & &\series{\iota} \arrow[ll, "\text{sum}"]

@@

On the other hand, we compute the asymptotic expansion of $I$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain. Consequently, its Borel transform $\series{\iota}$ is a germ of holomorphic functions at $\zeta=\alpha$ in the position domain. Finally, we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\series{\iota}_\alpha$.

@@

%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}

@@

%\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket

@@

%\item {[Thm 2]}: The Borel sum of the formal solutions $\series{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 

@@

%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \series{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\

@@

%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \series{\phi}\arrow[llu, no head, tail]

@@

%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \series{I}_{\alpha}(z)\arrow[dd,"\borel"]\\

@@

%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \series{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]

@@

%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular. Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity. Hence $\Phi$ is Borel-regularizable. In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$. In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity. 
\subsection{Borel regularity for level~$1$ ODEs}
%
The study of irregular singular differential equations in the complex domain has a long history, and interesting phenoma distinguish irregular singular equations to regular singular ones. Already at the formal level, irregular singular ODEs have a distinguished behaviour, namely they admit divergent formal series solutions in the form of trans-monomials. In particular, for level $1$ ODEs of the kind we study in this paper, the Poincar\'e method gives an algorithm to compute formal solutions of $\mathcal{P}\Phi=0$, see~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Then, the main question is how to ``promote'' a formal solution to an analytic one, and here is where summability methods will play a r\^ole~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}. In fact, even if it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one (see~\cite[Chapter 14]{balser}). Then, the Ramis Index Theorem shows that the formal solutions $\series{\Phi}$ of $\mathcal{P}\Phi=0$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}. Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.

@@

\color{RoyalBlue}
From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\series{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\series{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}. Since the cirtical values are distinct, the transmonomials $\series{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame. Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}). To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}. For example, the Ramis Index Theorem shows that the $\series{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}. \textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]}

At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame. This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\series{\Psi}_\alpha$ (see Theorem~\ref{thm:soln_is_asymptotic}). Recall that the key aspect in the proof of our result~\cite[Theorem~4]{reg-sing-volterra} is going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$. Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange solves differential equations analytically in the position domain~\cite{malgrange--fourier}, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).

@@

When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, we have the bound

@@

    \[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi}\ast\borel_\zeta\series{\Psi}.\]

@@

&=\borel_\zeta\series{\Phi}\ast \borel_\zeta\series{\Psi}\,.

@@

\begin{theorem}[restatement of~\ref{thm:maxim}]\label{thm:maxim-proof}

@@

@@
